Precise Data Flow Analysis\\in the Presence of Correlated Method Calls

### 2015-03-08 sas2015/content/appendix.tex
moving table to appendix

\section*{Appendix}
In this appendix we present the proofs to the Lemmas introduced in Section~\ref{sec:cca} and the code discussed in Section~\ref{sec:collex}.

@@

>>>>

\section*{Appendix}
In this appendix we present the proofs to the Lemmas introduced in Section~\ref{sec:cca}, the table illustrating frequencies of correlated calls from Section~\ref{}, and the code discussed in Section~\ref{sec:collex}.

@@

\subsection{Correlated Calls Occurrences}
Table~\ref{tab:dacapostat} shows how often correlated calls occur in practice. The number of all call sites in a program is denoted as $C$. 
Polymorphic call sites are denoted as $C_P$, and correlated call sites as $C^\Subset$. The~number of classes~$T$ and the number of lines of code are shown in the last two columns.
The first four columns indicate the overall number of various call sites and correlated-call receivers in a program. 
The next three columns indicate the ratio of polymorphic to all call sites, the ratio of correlated to polymorphic call sites, and the ratio of correlated call sites to correlated-call receivers.
In this context, we deem a call site to be polymorphic if its statically computed call graph
contains edges from the call site to multiple target methods.
We deem a call site to be a correlated call site if it is polymorphic and there is
at least one other polymorphic call site on the same receiver.
\input{tables/stats}

### 2015-03-08 sas2015/content/example.tex
moving table to appendix

\subsection{Occurrences of Correlated Calls}
How often do correlated calls occur in practice? To assess the benefit of the correlated-calls analysis, we counted the number of correlated calls that occur in programs of the Dacapo benchmarks~\cite{blackburn2006dacapo}, using the WALA framework for static analysis on Java bytecode~\cite{fink2012wala}.
Our goal was to obtain an upper bound on the number of redundant IFDS-result nodes that could be potentially removed by our analysis. The results are shown in Table~\ref{tab:dacapostat}.

In the table, the number of all call sites in a program is denoted as $C$. 
Polymorphic call sites are denoted as $C_P$, and correlated call sites as $C^\Subset$. The~number of classes~$T$ and the number of lines of code are shown in the last two columns.
The first four columns indicate the overall number of various call sites and correlated-call receivers in a program. 
The next three columns indicate the ratio of polymorphic to all call sites, the ratio of correlated to polymorphic call sites, and the ratio of correlated call sites to correlated-call receivers.
In this context, we deem a call site to be polymorphic if its statically computed call graph
contains edges from the call site to multiple target methods.
We deem a call site to be a correlated call site if it is polymorphic and there is
at least one other polymorphic call site on the same receiver.

\input{tables/stats}

>>>>

\subsection{Occurrences of Correlated Calls}
How often do correlated calls occur in practice? To assess the benefit of the correlated-calls analysis, we counted the number of correlated calls that occur in programs of the Dacapo benchmarks~\cite{blackburn2006dacapo}, using the WALA framework for static analysis on Java bytecode~\cite{fink2012wala}.
Our goal was to obtain an upper bound on the number of redundant IFDS-result nodes that could be potentially removed by our analysis. The results are shown in Table~\ref{tab:dacapostat} in the Appendix.
